Usage metrics

### 2021-01-04 analysis/corpus.Rmd
Update undefined calls

KAGGLE <- filter(ALL_KAGGLE, evals > 0)
```

@@

```{r}
cran_all_funs <- sum(ALL_CRAN$funs_public) + sum(ALL_CRAN$funs_private)
cran_funs <- sum(CRAN$funs_public) + sum(CRAN$funs_private)
cran_funs_with_eval <- sum(CRAN$funs_with_eval)
cran_code <- sum(CRAN$package_code)
cran_all_code <- sum(ALL_CRAN$package_code)
cran_evals <- CRAN$evals
cran_evals_hit <- CRAN$evals_hit

overview_table(
  r("CRAN all packages", ALL_CRAN),
  r("CRAN packages", CRAN),
  r("CRAN packages ratio", ratio(CRAN, ALL_CRAN)),
  r("CRAN all code", cran_all_code),
  r("CRAN all r code", sum(ALL_CRAN$package_r_code)),
  r("CRAN all native code", sum(ALL_CRAN$package_native_code)),
  r("CRAN code", cran_code),
  r("CRAN code ratio", ratio(cran_code, cran_all_code)),
  r("CRAN all funs", cran_all_funs),
  r("CRAN funs", cran_funs),
  r("CRAN funs with eval", cran_funs_with_eval),
  r("CRAN funs with eval ratio", ratio(cran_funs_with_eval, cran_funs)),
  r("CRAN all funs with eval ratio", ratio(cran_funs_with_eval, cran_all_funs)),
  r("CRAN eval call sites", sum(cran_evals)),
  r("CRAN hit eval call sites", sum(cran_evals_hit)),
  r("CRAN hit eval call sites avg ratio", percent(mean(cran_evals_hit/cran_evals))),
  r("CRAN runnable scripts", sum(ALL_CRAN$runnable_files)),
  r("CRAN runnable code", sum(ALL_CRAN$runnable_code)),
  r("CRAN runnable code examples", sum(ALL_CRAN$runnable_code_examples)),
  r("CRAN runnable code tests", sum(ALL_CRAN$runnable_code_tests)),
  r("CRAN runnable code vignettes", sum(ALL_CRAN$runnable_code_vignettes)),
)
```

@@

>>>>

KAGGLE <- filter(ALL_KAGGLE, evals > 0)

UNDEFINED <- 
  read_fst(PACKAGE_UNDEFINED_FILE) %>% 
  as_tibble()
```

@@

### Cran

```{r}
cran_all_funs <- sum(ALL_CRAN$funs_public) + sum(ALL_CRAN$funs_private)
cran_funs <- sum(CRAN$funs_public) + sum(CRAN$funs_private)
cran_funs_with_eval <- sum(CRAN$funs_with_eval)
cran_code <- sum(CRAN$package_code)
cran_all_code <- sum(ALL_CRAN$package_code)
cran_evals <- CRAN$evals
cran_evals_hit <- CRAN$evals_hit
cran_runnable_code <- sum(ALL_CRAN$runnable_code)
cran_eval_calls <- sum(CRAN_eval_traces$nb_ev_calls)

overview_table(
  r("CRAN available packages", 15962), #length(available.packages()[,1])), # from the CRAN mirror
  r("CRAN all packages", ALL_CRAN),
  r("CRAN packages", CRAN),
  r("CRAN packages ratio", ratio(CRAN, ALL_CRAN)),
  r("CRAN all code", cran_all_code),
  r("CRAN all r code", sum(ALL_CRAN$package_r_code)),
  r("CRAN all native code", sum(ALL_CRAN$package_native_code)),
  r("CRAN code", cran_code),
  r("CRAN code ratio", ratio(cran_code, cran_all_code)),
  r("CRAN all funs", cran_all_funs),
  r("CRAN funs", cran_funs),
  r("CRAN funs with eval", cran_funs_with_eval),
  r("CRAN funs with eval ratio", ratio(cran_funs_with_eval, cran_funs)),
  r("CRAN all funs with eval ratio", ratio(cran_funs_with_eval, cran_all_funs)),
  r("CRAN eval call sites", sum(cran_evals)),
  r("CRAN hit eval call sites", sum(cran_evals_hit)),
  r("CRAN hit eval call sites avg ratio", percent(mean(cran_evals_hit/cran_evals))),
  r("CRAN runnable scripts", sum(ALL_CRAN$runnable_files)),
  r("CRAN runnable code", cran_runnable_code),
  r("CRAN runnable code examples", sum(ALL_CRAN$runnable_code_examples)),
  r("CRAN runnable code tests", sum(ALL_CRAN$runnable_code_tests)),
  r("CRAN runnable code vignettes", sum(ALL_CRAN$runnable_code_vignettes)),
  r("CRAN undefined", UNDEFINED),
  r("CRAN undefined ratio", ratio(nrow(UNDEFINED), cran_eval_calls))
)
```

@@

### All

```{r}
overview_table(
  r("Corpus code", kaggle_code + cran_runnable_code)
)
```
